---
title: "A Very Detailed Paper on the Soybean Complex"
author: "Mindy L. Mallory"
date: "November 6, 2017"
output: pdf_document
bibliography: references.bib
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(xtable)


# This code chunk will call the cleaning.R, pretesting.R, and analysis.R files to prepare the results to be displayed in the document. 

source('analysis/helper-scripts/cleaning.R')
source('analysis/helper-scripts/pretesting.R')
source('analysis/analysis.R')



```

# Introduction

The soybean complex consists of soybeans, soybean meal, and soybean oil. The relationships between these three price series are interesting to study because they are bound by a production relationship. 

# Literature Review

Both [@johnson1955estimates] and [@simon1999soybean] studied soybeans, but they found different things. 

# Methods

We will test all three prices for stationarity and then we will fit a Vector Autoregression or a Vector Error Correction Model based on our findings. 

$$Y= mX + b$$




# Results

We find that all the series are non-stationary. See table 1 for results of Augmented Dickey-Fuller tests for each series. Table 2 shows how the VAR model results came out. We find that the lagged coeficient for Meal in the Bean equation is `r round(varPrint[2,3], 2)`.

# Conclusions

This concludes our paper. Future research should do much more. The end. Really the end. 

\pagebreak

# Tables and Figures

### Table 1: Augmented Dickey-Fuller Tests for each series
```{r, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}
rownames(adfResults) = c("Beans", "Meal", "Oil")

print(xtable(adfResults[,c(1,2)]), comment=FALSE)

```


### Table 2: Vector Autogressive Model Results 


```{r, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}
print(xtable(varPrint), comment=FALSE, include.rownames=FALSE)
```

\pagebreak

### Figure 1: Prices

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width = 6, fig.height = 9}
library(ggplot2)
library(gridExtra)
b <- autoplot(data$Beans) + theme_bw() + ylab("cents/bushel") + xlab("") + ggtitle("Beans")
m <- autoplot(data$Meal) + theme_bw() + ylab("$/ton") + xlab("") + ggtitle("Meal")
o <- autoplot(data$Oil) + theme_bw() + ylab("cents/bushel") + xlab("") + ggtitle("Oil")
grid.arrange(b, m, o)
```
\pagebreak



# References

