---
title: "A Very Detailed Paper on the Soybean Complex"
author: "Mindy L. Mallory"
date: "November 6, 2017"
output: pdf_document
bibliography: references.bib
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(xtable)


# This code chunk will call the cleaning.R, pretesting.R, and analysis.R files to prepare the results to be displayed in the document. 

source('analysis/helper-scripts/cleaning.R')
source('analysis/helper-scripts/pretesting.R')
source('analysis/analysis.R')



```

# Introduction

The soybean complex consists of soybeans, soybean meal, and soybean oil. The relationships between these three price series are interesting to study because they are bound by a production relationship. 

# Literature Review

Both [@johnson1955estimates] and [@simon1999soybean] studied soybeans, but they found different things. 

# Methods

We will test all three prices for stationarity and then we will fit a Vectro Autoregression or a Vector Error Correction Model based on our findings. 


# Results

We find that all the series are non-stationary. See table 1 for results of Augmented Dickey-Fuller tests for each series. 



# Tables and Figures

### Table 1: Augmented Dickey-Fuller Tests for each series
```{r, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}
rownames(adfResults) = c("Beans", "Meal", "Oil")

print(xtable(adfResults[,c(1,2)]), comment=FALSE)

```




# References

